Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2015-04-17 tex/ms.tex
tex updates for GGC data

% ---- Charlie (emulateapj) mode ----
 \documentclass[iop,numberedappendix]{emulateapj}
 \usepackage{apjfonts}
% ----
\usepackage{color, hyperref}
\bibliographystyle{apj}
\input{vc}

@@

The Right Thing To Do is to express the \emph{reason} that the RPI
believes the spectroscopic data to be less reliable \emph{within} the
likelihood function.
That is, the RPI must add nuisance parameters to parameterize the
unreliability of the spectroscopy, and infer those along with the
parameters of interest.
If this parameterization is good, the information in the spectroscopy
data will not flow entirely to the parameters of interest; instead,
some will flow to the nuisance parameters.
This will reduce the importance of the spectroscopy relative to the
photometry and the RPI will be well pleased with the dominance of the
photometric data in the final inferences of the parameters of
interest.
In what follows, we provide an example of this kind of
parameterization and inference.

@@

If you don't believe the reported data noise variances $\sigma_n^2$,
it often makes sense to add in quadrature a ``jitter'' variance $s^2$.
This is a trivial modification of the chi-squared log-likelihood:
\begin{eqnarray}\label{eq:photometricLF}
\ln p(d\given\theta,s^2) &=& -\frac{1}{2}\,\sum_{n=1}^N \left[\frac{[d_n - \mu_n(\theta)]^2}{[\sigma_n^2 + s^2]} + \ln(2\pi\,[\sigma_n^2 + s^2]) \right]
\quad .
\end{eqnarray}
This modification shows the necessity of including the log-variance
term.
This---equation~(\ref{eq:photometricLF})---is in fact the
log-likelihood function we are going to use for the photometric
measurements ({\color{blue} BDJ: IS THIS TRUE?} {\color{red} Jitter
will be added now with correct sign as I test increases in model
complexity }) in what follows.  
In this formulation, if $\theta$ are the parameters of interest, the
jitter variance $s^2$ is a nuisance noise-model parameter.  The
Gaussian Process will be a generalization of this modification.

We take the calibration-vector that modifies the mean model to produce
the observed spectrum as multiplicative with respect to the mean
model.  In this case we define the residual of the data from the model
in terms of the logarithmic differences.  This logarithmic formulation
requires that $d$ be everywhere positive, and distorts the
uncertainties, especially at low S/N ratio.  The advantages of
defining the residual in this way are that the model remains linear
(and therefore fast) and the calibration vector is forced to be
positive everywhere.  However, at high signal to noise the distortion
of the uncertainties will be minimal.

@@

@@

We are now left to demonstrate that, by including photometry as well
as spectroscopy, it is possible to infer the parameters of interest
$\theta$ while marginalizing over the calibration parameters $\alpha$.
We will apply the methodology for spectrophotometric calibration
described above to \emph{actual, real} optical spectra of a stellar
clusters in M31.  Spectra of star clusters provide a good test case,
as they are less complex than galaxy spectra (for which it is
necessary to model the star formation history) but are by no means
trivial. In this way the key features of the calibration model and
methodology are not obscured.

To demonstrate the effectiveness of our strategy for combining
spectroscopic and photometric information we will infer the parameters
$\theta$ from a spectrum both \emph{before} and \emph{after} it has
been spectrophotometrically calibrated using typical techniques and
ancillary spectrophotometric calibration data.

\begin{figure}[h!]
\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
\caption{The calibrated (left) and uncalibrated (right) spectrum for
\excluster, along with the uncertainties (bottom panel). The spectra
have been renormalized to avoid floating point errors. {\color{blue}
SHOULD THIS SHOW ALL THE CLUSTERS OR JUST ONE?.}\label{fig:data}}
\end{figure}

@@

\item We should test on fake data, with known squiggly
  calibration applied, to demonstrate that we can infer the
  calibration vector and the physical parameters with no bias.  We
  should use the squiggly calibration derived from one of Nelson's
  calibrated/uncalibrated spectra.  We should also do this for
  differnt S/N to find where the logarithmic residual formulation
  breaks down.

\item We infer the parameters of the spectrum of a real cluster that
has been photometrically calibrated. Then, we infer the parameters of
the spectrum of the same cluster \emph{without} spectrophotometric
calibration, to see if we infer physical parameters consistent with
the calibrated case.  How many/which figures to show?

\item  Then, we show select marginalized or joint PDFs for many
clusters calibrated/uncalibrated, to assess consistency.  Or we just
show comparisons of confidence intervals for the parameters of a
number of clusters, calibrated/uncalibrated.

\item We infer the parameters of the calibrated spectrum without
including the noise model, or presumably the photometry (since
reconciling photometry and spectroscopy is done by our noise model).
What changed, what did we get wrong without the noise model?
{\color{blue} Should we keep the $f(\alpha)$ and the photometry?  This
just has the potential to show shortcomings in the spectrophotometric
calibration}

\item Finally, we change the number of photometric bands and see what
happens to the inferred parameters, using the full model.

@@

The data we use to test our method consist of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-9100$\AA. The instrumental resolution is
$\sim 5$\AA~ across the optical range \citep{fabricant13}.  {\color{blue} Wavelength
calibration happened. Sky subtraction happened.} The data were
approximately spectrophotometrically calibrated using an average
calibration vector for the night constructed from {\color{blue} MORE
HERE. Discuss S/N, sky subtraction.}

An example spectrum, both after and before spectrophotometric
calibration, is shown in Figure \ref{fig:data}.  When fitting the
spectra we mask the region around the bright OI5577 sky line, and we
fit only to the spectrum with $3750 < \lambda < 7200$\AA~ to avoid the low
S/N edges and, on the red side, imperfect sky line subtraction in a
region of the spectrum that has a paucity of informative spectral
lines. Furthermore, the MILES spectral library (see
\S\ref{sec:cluster_model}) only extends to $\lambda < 7500$\AA.
{\color{red} Specify/Justify order of calibration polynomial here?}.

{\color{blue} DRW words about photometry}

@@

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle
F_{\theta^\prime}(\lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta^\prime$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$, 
luminosity distance $d_L$,
and redshift $z$.  
The observed frame wavelengths $\lambda_o$ are related to the restframe
wavelengths $\lambda$ in the usual way.

The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$.
Here the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks. We will assume
$\beta$ to be fixed for the purposes of this exercise, with no loss of
generality {\color{blue} (KEEPING IMF SLOPE CONSTANT)}.  We will also
fix the shape of the attenuation curve, $k_\lambda \equiv
\tau_\lambda/\tau_V$, to the Milky way average of \citet{CCM89} with
$R_V=3.1$ and assume that $d_L$ is known to high precision from
independent methods and can therefore be treated as fixed.  In
practice, $d_L$ is completely degenerate with $m_*$. We calculate
$S(\lambda, t, Z)$ using the Flexible Stellar Population Synthesis
code \citep[FSPS][]{fsps}.  We use the Padova 2007 isochrones
\citep{girardi00, bertilli94, marigo07} and the MILES stellar spectral
library \citep{miles_I, miles_II, miles_III}.

The model spectra $F_{\theta^\prime}$ are smoothed by convolution
with a Gaussian in wavelength space (in this case to model the MMT
line-spread function) and are interpolated to the wavelength points of
the of the observed spectrum while taking into account the
redshift. The instrumental resolution is given by the parameter
$\sigma$.  {\color{blue}Discuss intrinsic resolution of model spectra
(MILES), what to do in situations where instrumental resolution is
higher, lower or comparable (ouch) to intrinsic velocity broadening.}

@@

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell(\lambda) \\
S_\ell (\lambda) & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G_\sigma$ represents a Gaussian of unit area 
and standard deviation $\sigma$, 
$\otimes$ indicates convolution, 
and the full parameter set $\theta$ now includes
the instrumental wavelength broadening $\sigma$ 
and the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular emission and interstellar
absorption lines.
This is the mean model which appears in equation
\ref{eq:spectroscopicLF}.

@@

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Spectra resulting from draws from the posterior parameter
space conditioned on the calibrated \excluster~ spectrum and
photometry.  Left: For each of 5 draws from the posterior we show from
top to bottom, three components of the model: the mean cluster
spectrum, the calibration vector, and the mean prediction of $\Delta$
for the Gaussian process.  Right: From top to bottom, the full model
({\it magenta}) compared to the observed, calibrated spectrum ({\it
grey}), the ratio of the observed to the modeled spectrum, and the
difference between the observed spectrum and the modeled spectrum
normalized by the uncertainty.
\label{fig:inferred_spectrum}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/zfig_b192-g242_225_cal.png}
\caption{Zoom-in on selected regions of the observed spectrum, showing
also draws from the posterior model for the spectra in these regions
and residulas of these draws from the observations.
\label{fig:zoom_spectrum}}
\end{figure*}

@@

\begin{figure}[h!]
\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
\caption{ Model SEDs.  Top: The model photometric SED resulting from
draws from the posterior parameter space conditioned ({\it cyan}) on
the observed photometry ({\it magenta}) and spectra.  Bottom:
uncertainty normalized residuals of the models from the observations.
\label{fig:inferred_sed}}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
\caption{ Marginalized and joint PDFs of subset of the physical
parameters $\theta$ inferred from the spectophotometrically calibrated
spectrum of \excluster. The blue lines indicate the parameter values
that resulted from the powell minimization.
\label{fig:inferred_params}}
\end{figure}

The physical model parameters that we infer indicate that \excluster~
has super-solar metallicity, an age of $\sim 225$ Myr, moderate dust
extinction, and a stellar mass of $\sim 10^{4}$ M$_{sun}$ {\color{blue}
check that this is current mass, not initial mass}.  We find a spectral
broadening of $\sim 1.75$\AA~ (4.1\AA~ FWHM), which when combined in
quadrature with the intrinsic resolution of the MILES library, 2.5\AA~
FWHM \citep{beifiori11}, reproduces the typical line-spread function
of the MMT Hectospec instrument, $\sim 5$\AA~ \citep{fabricant13}.
We obtain strong constraints on the systemic velocity.

It is possible to reconstruct the inferred total multiplicative
calibration vector for each draw of the model parameters.  Rearranging
equation \ref{eq:spectroscopicLF} yields
\begin{eqnarray} 
\frac{d}{\mu(\theta)} & = & exp(f(\alpha) + \tilde{\Delta})
\quad ,
\end{eqnarray}
for the total effective multiplicative calibration, where
$\tilde{\Delta}$ is now the Gaussian process mean prediction for the
logarithmic residual between the data and the model. The inverse of
this ratio is shown in the left panel of Figure
\ref{fig:inferred_calib} as our inferred total multiplicative
calibration function; if the spectrophotometric calibration were
perfect and we had correctly inferred it, then we would expect this
vector to be constant as a function of wavelength.

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
\caption{Left: Samples of the effective multiplicative calibration
vector for the spectrophotometrically calibrated spectrum of
\excluster~ ({\it cyan}) compared to that obtained from ancillary
photometric data ({\it magenta}).  
%Right: The same, but for the uncalibrated data.
 \label{fig:inferred_calib}}
\end{figure*}

@@

We have demonstrated, using a sample of stellar clusters in M31, that
we can combine photometric and spectroscopic data in a principled way
to infer physical properties.  We do not resort to an arbitrary
down-weighting or up-weighting of certain data. Instead, we explicitly
model our uncertain knowledge of the spectral calibration and infer
this calibration jointly with the physical properties. For a number of
applications this combination of spectroscopy and photometry reduces
the need for spectrophotometric calibration entirely, such that the less
expensive photometric calibration is sufficient.  Additional calibration
information, if it exists, can be incorporated into informative priors
on the calibration parameters of the model, inform the construction
of the calibration model, or approximately remove gross features
that are difficult to model parameterically or as a sum of Gaussians.

{\color{blue} BDJ words about the gains that might be made by
including photometry over a large range in wavelngth with spectroscopy
over relatively small ranges.}

Our strategy is easily extensible to more complicated models, which
include for example night sky-line emission in the spectroscopy (or
residuals from an intial sky-line subtraction), and uncertainties in
wavelength calibration. Furthermore, more complex physical models may
be considered for the mean object model, for example including SFH
parameters so as to model galaxies.  {\color{blue} DISCUSS MORE
COMPLICATED COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL
CHECKING. As I understand it, additional `bad lines' in the mean model
could be accounted for using narrow quadratics in the covariance
matrix, though their interpretation would be hellish. The best way is
probably to explictly model them in the mean model}

@@

All the code used in this project is available under an open-source license
  from \url{http://github.com/bd-j/bsfh/}.
This version of the paper was generated
  from a git repository available at \url{http://github.com/bd-j/speccal/}
  with git hash \texttt{\githash\,(\gitdate)}.

@@

@@

\bibitem[Fabricant \etal(2013)]{fabricant13} 
Fabricant, D., Chilingarian, I., Hwang, H.~S., et al.\ 2013, \pasp, 125, 1362

@@

>>>>

% ---- Charlie (emulateapj) mode ----
 \documentclass[iop,numberedappendix]{emulateapj}
 \usepackage{apjfonts}
% ----
\usepackage{color, hyperref}
\bibliographystyle{apj}
%\input{vc}

@@

The Right Thing To Do is to express the \emph{reason} that the RPI
believes the spectroscopic data to be less reliable \emph{within} the
likelihood function.
That is, the RPI must add nuisance parameters to parameterize the
unreliability of the spectroscopy, and infer those along with the
parameters of interest.
If this parameterization is good, the information in the spectroscopy
data will not flow entirely to the parameters of interest; instead,
some will flow to the nuisance parameters.
This will reduce the importance of the spectroscopy relative to the
photometry and the RPI will be well pleased with the dominance of the
photometric data in the final inferences of the parameters of
interest.
This amounts to propogating the uncertainties in the
spectrophotometric calibration (or alternatively in the continuum
normalization).
In what follows, we provide an example of this kind of
parameterization and inference.

@@

If you don't believe the reported data noise variances $\sigma_n^2$,
it often makes sense to add in quadrature a ``jitter'' variance $s^2$.
This is a trivial modification of the chi-squared log-likelihood:
\begin{eqnarray}\label{eq:photometricLF}
\ln p(d\given\theta,s^2) &=& -\frac{1}{2}\,\sum_{n=1}^N
                             \left[\frac{[d_n -
                             \mu_n(\theta)]^2}{[\sigma_n^2 + (s\, \mu_n(\theta))^2]} + \ln(2\pi\,[\sigma_n^2 + s^2]) \right]
\quad .
\end{eqnarray}
This modification shows the necessity of including the log-variance
term.
This---equation~(\ref{eq:photometricLF})---is in fact the
log-likelihood function we are going to use for the photometric
measurements in what follows.  
In this formulation, if $\theta$ are the parameters of interest, the
jitter variance $s^2$ is a nuisance noise-model parameter representing
additonal fractional uncertainty in the flux.  The
Gaussian Process will be a generalization of this modification.

We take the calibration-vector that modifies the mean model to produce
the observed spectrum as multiplicative with respect to the mean
model.  In this case we define the residual of the data from the model
in terms of the logarithmic differences.  This logarithmic formulation
requires that $d$ be everywhere positive, and distorts the
uncertainties, especially at low S/N ratio.  The advantages of
defining the residual in this way are that the model remains linear
(and therefore fast) and the calibration vector is forced to be
positive everywhere.  Additionally, at high signal to noise the distortion
of the uncertainties will be minimal.

@@

XXX Alternative XXX
To avoid making the logarithmic transform described above, which
distorts the errors, we can formulate the problem in a different way,
modifying Equation \label{eq:spectroscopicLF} above as 
\begin{eqnarray}\label{eq:spectroscopicLF_v2}
\ln p(d\given\theta,\alpha) &=& -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta + \ln([2\pi]^N\,\det{C}) \right]
\\
\Delta &\equiv& d - \mu(\theta) * f(\alpha) 
\\
C_{nn'} &\equiv& [\sigma_n^2 + (s * \mu)^2]\,\delta_{nn'} +
\transpose{\mu} \, K_\alpha(\lambda_n - \lambda_{n'}) \, \mu
\quad ,
\end{eqnarray}
where the multiplication of $s$ and $K_\alpha$ by $\mu$ in the
construction of $C_{nn'}$ means that they are defined in
\emph{fractional} terms, and the uncertainties remain Gaussian in
linear flux space.  It remains to be seen whether this actually works.

@@

We are now left to demonstrate that, by including photometry as well
as spectroscopy, it is possible to infer the parameters of interest
$\theta$ while marginalizing over the calibration parameters $\alpha$.
We will apply the methodology for spectrophotometric calibration
described above to both \emph{mock} and \emph{real} optical spectra of
Galactic globular clusters.  Spectra of globular clusters provide a good test case,
as they are less complex than galaxy spectra (for which it is
necessary to model the star formation history) but are by no means
trivial. In this way the key features of the calibration model and
methodology are not obscured.  Additionally, information
about the physical parameters of the cluster is available from
resolved stellar CMDs, providing an important check on our inference methodology
and especially our population synthesis models.

The separate treatment of mock and real data allows us to address two
separate issues.  The inference from mock data (with a realistic
calibration vector applied) provides a test of the methodology and the
effect of calibration uncertainties on the inferred parameters in the
case of a perfect mean model $mu(\theta)$.  The inference from real
data tests a combination of our methodology and the ability of the
population synthesis models to recover parameters inferred from
resolved star CMDs (i.e. some estimate of ground truth)

To demonstrate the effectiveness of our strategy for combining
spectroscopic and photometric information we will infer the parameters
$\theta$ from a spectrum both \emph{before} and \emph{after} it has
been spectrophotometrically calibrated using and
ancillary spectrophotometric calibration data.

\begin{figure}[h!]
%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
\caption{The calibrated spectrum for \excluster, along with the
uncertainties (bottom panel).The right panel shows the
spectrophotometric calibration vector determined by
\citet{schiavon05}. \label{fig:data}}
\end{figure}

@@

\item Mock perfectly calibrated data: inference using spectroscopy and one
  photometric band, with both full calibration model and assuming no
  calibration uncertainty.

\item Mock uncalibrated data:  inference using spectroscopy and one
  photometric band, with full calibration model

\item Mock data: inference using photometry only, full spectroscopic model

\item Mock uncalibrated data: inference using spectroscopy and all
  photometry, full calibration model.

\item Mock perfectly calibrated data: inference using spectroscopy and all
  photometry, with both full calibration model and assuming no
  calibration uncertainty.

\item Real calibrated spectrum:   Inference using spectroscopy and all
  photometry, with full calibration model.

\item Real uncalibrated spectrum:   Inference using spectroscopy and all
  photometry, with full calibration model.

\item Compare the physical parameters inferred from from the real
  calibrated and uncalibrated spectrum with each other and with CMD
  based parameters.

@@

The data we use to test our method consist of optical spectroscopy of
of galactic globular clusters from \citet{schiavon05} for which
optical and NIR photometry are availbale. The optical spectra were
obtained by drift-scanning a long-slit spectrograph across the
cluster.  The wavelength range of the spectra is $3500-6500$\AA. The
instrumental resolution is $\sim 3.1$\AA~ at $\sim 4500\AA$ and varies
with wavelength.  These spectra have been placed on the rest-frame,
though in what follows we will model the effect of redshift
uncertainties on the data.

An example spectrum (and the inferred spectrophotometric calibration
vector) is shown in Figure \ref{fig:data}.  As stated by
\citet{schiavon05}, the spectrophotometric calibration of these data are
only approximate.  When fitting the spectra we mask the region around
the bright OI5577\AA~ sky line, and we fit only to the spectrum with $3550\AA
< \lambda < 6500$\AA~ which are covered by the MILES spectral library
(see \S\ref{sec:cluster_model}).  Absorption lines of the interstellar
medium (ISM) can significantly affect the spectrum, so we
additionally mask the Calcium H and K lines and the NaD doublet.

Words about photometry

@@

\subsection{Mock Data}
Our mock data are designed to mimic the actual data as much as
possible.  Mock spectra and photometry are generated from the model
below for a given set of parameters $\theta^\prime$.  We then convolve
the spectrum with an instrumenal LSF, interpolate onto the observed
wavelength scale and add noise according to the
SNR of the real data.  For the photometry we assume a SNR of 10.  We
also mask the mock spectra at the location of significant sky lines
and ISM lines.

The mock spectrum is shown in Figure \ref{fig: mock spectrum}.  We
will refer to this spectrum as the \emph{perfectly calibrated}
mock spectrum.  We also produce a mock spectrum by dividing this
perfectly calibrated spectrum by the spectrophotometric calibration vector
taken from the real data
\citep[][Fig\ref{fig:ggc_spectrum}]{schiavon05}, which we refer to as
the \emph{uncalibrated} mock spectrum.

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle
F_{\theta^\prime}(\lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta^\prime$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$, 
luminosity distance $d_L$,
and redshift $z$.
The shape of the dust attenuation curve is given by $k_\lambda \equiv
\tau_\lambda/\tau_V$.  
The observed frame wavelengths $\lambda_o$ are related to the
restframe wavelengths $\lambda$ in the usual way.

The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$.
Here the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks. We will assume
$\beta$ to be fixed for the purposes of this exercise, with no loss of
generality but significant savings in computational time.  We will
also fix the shape of the attenuation curve, $k_\lambda $, to the
Milky way average of \citet{CCM89} with $R_V=3.1$ and assume that
$d_L$ is known to high precision from independent methods and can
therefore be treated as fixed.  In practice, $d_L$ is prefectly
degenerate with $m_*$. We calculate $S(\lambda, t, Z)$ using the
Flexible Stellar Population Synthesis code \citep[FSPS][]{fsps}.  We
use the Padova 2007 isochrones \citep{girardi00, bertilli94, marigo07}
and the MILES stellar spectral library \citep{miles_I, miles_II,
miles_III}.

@@

The model spectra $F_{\theta^\prime}$ are smoothed by convolution with
the line-spread function of the spectrograph and are interpolated to
the wavelength points of the of the observed spectrum while taking
into account the redshift. For computational simplicity we assume that
the internal velocity dispersion of the cluster is negligible compared
to the instrumental broadening, though in principle it can and should
also be modeled. he instrumental resolution is given by the parameter
$\sigma$.  {\color{blue}Discuss intrinsic resolution of model spectra
(MILES), what to do in situations where instrumental resolution is
higher, lower or comparable (ouch) to intrinsic velocity broadening.}

The final mean model is then given by the convolution in wavelength
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (LSF(\sigma_{inst}) \otimes F(\theta^\prime))(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell(\lambda) \\
S_\ell (\lambda) & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
\lambda_\ell)^2}{2\sigma_e^2}) \\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma_{inst}, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right] \\
\quad ,
\end{eqnarray}
where $LSF(\sigma_{inst})$ represents the linespread function
parameterized by $\sigma_{inst}$, 
$\otimes$ indicates convolution, 
and the full parameter set $\theta$ now includes
the instrumental broadening $\sigma_{inst}$ 
and the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular emission and interstellar
absorption lines.
This is the mean model which appears in equation
\ref{eq:spectroscopicLF}.

@@

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Spectra resulting from draws from the posterior parameter
space conditioned on the calibrated \excluster~ spectrum and
photometry.  Left: For each of 5 draws from the posterior we show from
top to bottom, three components of the model: the mean cluster
spectrum, the calibration vector, and the mean prediction of $\Delta$
for the Gaussian process.  Right: From top to bottom, the full model
({\it magenta}) compared to the observed, calibrated spectrum ({\it
grey}), the ratio of the observed to the modeled spectrum, and the
difference between the observed spectrum and the modeled spectrum
normalized by the uncertainty.
\label{fig:inferred_spectrum}}
\end{figure*}

@@

It is possible to reconstruct the inferred total multiplicative
calibration vector for each draw of the model parameters.  Rearranging
equation \ref{eq:spectroscopicLF} yields
\begin{eqnarray} 
\frac{d}{\mu(\theta)} & = & e^{f(\alpha) + \tilde{\Delta}}
\quad ,
\end{eqnarray}
for the total effective multiplicative calibration, where
$\tilde{\Delta}$ is now the Gaussian process mean prediction for the
logarithmic residual between the data and the model. The inverse of
this ratio is shown in the left panel of Figure
\ref{fig:inferred_calib} as our inferred total multiplicative
calibration function; if the spectrophotometric calibration were
perfect and we had correctly inferred it, then we would expect this
vector to be constant as a function of wavelength.

\begin{figure}[h!]
%\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
\caption{ Model SEDs.  Top: The model photometric SED resulting from
draws from the posterior parameter space conditioned ({\it cyan}) on
the observed photometry ({\it magenta}) and spectra.  Bottom:
uncertainty normalized residuals of the models from the observations.
\label{fig:inferred_sed}}
\end{figure}

\begin{figure}[h!]
%\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
\caption{ Marginalized and joint PDFs of subset of the physical
parameters $\theta$ inferred from the spectophotometrically calibrated
spectrum of \excluster. The blue lines indicate the parameter values
that resulted from the powell minimization.
\label{fig:inferred_params}}
\end{figure}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
\caption{Left: Samples of the effective multiplicative calibration
vector for the spectrophotometrically calibrated spectrum of
\excluster~ ({\it cyan}) compared to that obtained from ancillary
photometric data ({\it magenta}).  
Right: The same, but for the uncalibrated data.
 \label{fig:inferred_calib}}
\end{figure*}

@@

We have demonstrated, using using both mock and real spectra of
galactic stellar clusters, that we can combine photometric and
spectroscopic data in a principled way to infer physical properties.
We do not resort to an arbitrary down-weighting or up-weighting of
certain data. Instead, we explicitly model our uncertain knowledge of
the spectral calibration and infer this calibration jointly with the
physical properties. For a number of applications this combination of
spectroscopy and photometry reduces the need for spectrophotometric
calibration entirely, such that the less expensive photometric
calibration is sufficient.  Additional calibration information, if it
exists, can be incorporated into informative priors on the calibration
parameters of the model, inform the construction of the calibration
model, or approximately remove gross features that are difficult to
model parameterically or via a Gaussian Process.

{\color{blue} BDJ words about the gains that might be made by
including photometry over a large range in wavelength with spectroscopy
over relatively small ranges.}

{\color{blue} BDJ BDJ discuss the relation of this technique to the typical use of
continuum normalization when fitting spectroscopy.}

Our strategy is easily extensible to more complicated models, which
include for example night sky-line emission in the spectroscopy (or
residuals from an intial sky-line subtraction), and uncertainties in
wavelength calibration. Furthermore, more complex physical models may
be considered for the mean object model, for example including SFH
parameters so as to model galaxies.  {\color{blue} DISCUSS MORE
COMPLICATED COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL
CHECKING.}

@@

All the code used in this project is available under an open-source license
  from \url{http://github.com/bd-j/bsfh/}.
%This version of the paper was generated
%  from a git repository available at \url{http://github.com/bd-j/speccal/}
%  with git hash \texttt{\githash\,(\gitdate)}.

@@

\bibitem[Becker et al.(2015)]{becker15} Becker, J.~C., Johnson, 
J.~A., Vanderburg, A., \& Morton, T.~D.\ 2015, arXiv:1503.03874

@@

%\bibitem[Fabricant \etal(2013)]{fabricant13} 
%Fabricant, D., Chilingarian, I., Hwang, H.~S., et al.\ 2013, \pasp, 125, 1362

@@

\bibitem[Schiavon et al.(2005)]{schiavon05} Schiavon, R.~P., Rose, 
J.~A., Courteau, S., \& MacArthur, L.~A.\ 2005, \apjs, 160, 163

\bibitem[Sch{\"o}nrich 
\& Bergemann(2014)]{schonrich14} Sch{\"o}nrich, R., \& Bergemann, M.\ 2014, \mnras, 443, 698
